\chapter{Homework 5: Blizzard Gear Web Site Usability Test}
	\section{Results}
		\begin{itemize}
			\item \textbf{Website:} \url{http://gear.blizzard.com/}
		\end{itemize}

		Blizzard is one of the greatest enterprises of electronic games of the United States and the Blizzard Gear is its main E-Store.

		The answers described below can be summarized as: The website is well designed and have good usability, but the color scheme could be better, specially the background color. Lacks a category about Action Figures.

	\section{Questions \& Answers}
		\subsection{General Information}
			\begin{enumerate}
				\item{\textbf{What is your full name?}
				\begin{enumerate}
					\item Ian Dias de Souza Pierson
					\item Julio Cesar Santos Ferrari
				\end{enumerate}
				}
				\item{\textbf{What is your Indiana Tech ID?}
				\begin{enumerate}
					\item 1618890
					\item 2619236
				\end{enumerate}
				}
				\item{\textbf{What is your major?}
				\begin{enumerate}
					\item Software Engineering
					\item Electrical Engineering
				\end{enumerate}
				}
			\end{enumerate}
		\subsection{Usability Test}
			\begin{enumerate}
				\item{\textbf{What is is the name of the business?}
				\begin{enumerate}
					\item Blizzard Gear
					\item Gear Blizzard
				\end{enumerate}
				}
				\item{\textbf{What is the nature of the business site? What are they selling?}
				\begin{enumerate}
					\item Store, Blizzard Collectibles
					\item Clothes, books and accesssories related to Blizzard Universe
				\end{enumerate}
				}
				\item{\textbf{What is the price of the Gryphon Hatchling Plush?}
				\begin{enumerate}
					\item[(a \& b)] \$ 25.00
				\end{enumerate}
				}
				\item{\textbf{Complete the following task using only clicks and write down how many clicks you did: Find the most expensive Heroes of the Storm product.}
				\begin{enumerate}
					\item[(a \& b)] 3
				\end{enumerate}
				}
				\item{\textbf{What is the price of the most expensive Heroes of The Storm product?}
				\begin{enumerate}
					\item[(a \& b)] \$ 79.99
				\end{enumerate}
				}
				\item{\textbf{Please give me your impressions about the layout of the Web site and what you think of the colors, graphics, photos, etc.}
				\begin{enumerate}
					\item I didn't like the background.
					\item Nice interface, easy usage. Could have more photos of each product.
				\end{enumerate}
				}
				\item{\textbf{If you could make one significant change to this Web site, what change would you make?}
				\begin{enumerate}
					\item Background change.
					\item Action figures category.
				\end{enumerate}
				}
			\end{enumerate}
